---
title: "Introduction to cumulocityr"
output:
  html_document:
    theme: cerulean
    highlight: textmate
    fig_width: 6
    fig_height: 4
    toc: true
    toc_depth: 2
vignette: >
  %\VignetteIndexEntry{Introduction to cumulocityr}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(cumulocityr)
library(knitr)

```


### Authentication

Credentials and url for cumulocity are stored in a user's private `.Renviron` file.



### Get devices

Get devices for the tenant and display a few columns. If no arguments are passed, `get_devices()` returns all devices.

```{r}
devices <- get_devices()
print(devices[,c("type", "name", "id")])
```


### Get measurements

Get measurements for device "Temperature #1" and plot the result.
```{r}

meas <- get_measurements(device_id = 53700,
                         num_rows = 100,
                         date_from = "2019-09-30T19:59:00Z")
kable(head(meas[c("time", "type", "c8y_Temperature.T.value")]))

plot(meas$time, meas$c8y_Temperature.T.value, type = "l",
     xlab = "Time", ylab = "Temperature (deg C)")

```


### Get events

Similarly, we can get events for the same device:
```{r}

events <- get_events(device_id = 53700,
                     num_rows = 6,
                     date_from = "2019-09-30T19:59:00Z")

kable(events[c("type", "time", "c8y_Position.lng", "c8y_Position.alt")])
```

### Unparsed data

By default, the content is parsed, but it is possible to return a list of JSON objects.
```{r}
meas_03 <- get_measurements(device_id = 53700,
                            num_rows = 2,
                            date_from = "2019-09-30T19:59:00Z",
                            parse_json = FALSE)

print(meas_03)
```
